### 2023-02-23 talk/talk.tex
a few talk edits

\begin{frame}{Pre-vaccination weakly measles in England \& Wales}

@@

@@

  \begin{itemize}
  \item EnKF is based on a continuous Gaussian approximation.
  \item Log-likelihoods with respect to counting measure are never positive, and cannot properly be compared with log-likelihoods corresponding to continuous densities.
    \item For data with many zeros, the unbounded EnKF likelihood can substantially bias the MLE.
    \item Adapting EnKF for count data is non-trivial (Katzfuss et al, {\it JASA}, 2019).
    \item Li et al avoided the issue by using a ``heuristic observation error variance'' within EnKF. The corresponding ``log-likelihood'' is not the log-likelihood of any model. In particular, it cannot validly be compared againt simple statistical benchmarks.
  \item Data and models will never be perfect. We want to reveal, rather than conceal, limitations.
  \end{itemize}

@@

  \item The \texttt{spatPomp} package facilitates data analysis.

    \item Questions and comments?

>>>>

\begin{frame}{Pre-vaccination weekly measles in England \& Wales}

@@

  %%% Haiti and Dominican Republic share Hispaniola

@@

  \begin{itemize}
  \item EnKF is based on a continuous Gaussian approximation.
  \item Log-likelihoods with respect to counting measure are never positive, and cannot properly be compared with log-likelihoods corresponding to continuous densities.
    \item For data with many zeros, the unbounded EnKF likelihood can substantially bias the MLE.
    \item Adapting EnKF for count data is non-trivial (Katzfuss et al, {\it JASA}, 2019).
%    \item Li et al avoided the issue by using a ``heuristic observation error variance'' within EnKF. The corresponding ``log-likelihood'' is not the log-likelihood of any model. In particular, it cannot validly be compared againt simple statistical benchmarks.
%  \item Data and models will never be perfect. We want to reveal, rather than conceal, limitations.
  \end{itemize}

@@

  \item As long as the \texttt{spatPomp} package facilitates data analysis, we expect continuing package development.

%    \futuresep

 %   \item Questions and comments?
